\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-09-13 paper/ms.tex
Mac OS X thing
Correction

@@

\subsection{ABC example results}
For ABC applications, there is an alternate \code{postprocess} function
called \code{postprocess_abc}.
This generates posterior samples using the $\epsilon$ value that
compresses the joint prior by 80\% as much as the final level.
\begin{CodeChunk}
\begin{CodeInput}
dnest4.postprocess_abc()
\end{CodeInput}
\end{CodeChunk}
To try different values of $\epsilon$, you can set the argument
\code{threshold\_fraction} to a value other than 0.8. For example
\begin{CodeChunk}
\begin{CodeInput}
dnest4.postprocess_abc(threshold_fraction = 0.6)
\end{CodeInput}
\end{CodeChunk}

>>>>

In Mac OS X, the final line might need to provide information about
your OS version, like so:

\begin{CodeChunk}
\begin{CodeInput}
> MACOSX_DEPLOYMENT_TARGET=10.9 python setup.py install
\end{CodeInput}
\end{CodeChunk}

@@

\subsection{ABC example results}
For ABC applications, there is an alternate \code{postprocess} function
called \code{postprocess_abc}.
This generates posterior samples using the $\epsilon$ value corresponding
to level $\approx$ 3/4$\times$ (maximum number of levels).
\begin{CodeChunk}
\begin{CodeInput}
dnest4.postprocess_abc()
\end{CodeInput}
\end{CodeChunk}
To try different values of $\epsilon$, you can set the argument
\code{threshold\_fraction} to a value other than 0.8. For example
\begin{CodeChunk}
\begin{CodeInput}
dnest4.postprocess_abc(threshold_fraction = 0.6)
\end{CodeInput}
\end{CodeChunk}
